\section{Tokenomics \& The MFAI Utility Model}

\subsection{Token Philosophy}
\mfaithink{"\$MFAI is not a speculative asset, but the programmable proof of cognitive value, reputation, and sovereignty."}

\begin{mfai-box}{Why Tokenize Cognition?}{}
The \mfaiconcept{Money Factory AI} protocol is built on the conviction that knowledge, creation, and contribution deserve on-chain capital and governance. The $MFAI token is not a mere utility: it is the economic engine and proof-of-value for every participant. Each $MFAI is \textbf{earned} through learning, building, and governance, not farmed or given away. It enables access, incentivizes effort, and anchors reputation in a living, meritocratic economy.
\end{mfai-box}

\subsection{Use Cases}
\begin{itemize}
    \item \faKey\quad \textbf{Access}: Unlock advanced features, NFT Passes (Gold, Platinum, Diamond), and \mfaiconcept{Zyno Pro} modules
    \item \faLock\quad \textbf{Staking (Cognitive Lock\texttrademark)}: Stake \$MFAI for governance, Launchpad priority, and yield
    \item \faGavel\quad \textbf{DAO Voting}: Participate in protocol decisions, project selection, and validation of \mfaiproof{Proofs}
    \item \faCertificate\quad \textbf{NFT Minting}: Required for \mfaiproof{Proof-of-Skill\texttrademark} and \mfaiproof{Proof-of-Vision\texttrademark} credentials
    \item \faChartLine\quad \textbf{Neuro-Dividends\texttrademark}: Earn protocol revenue streams based on contribution and staking
    \item \faRocket\quad \textbf{Premium Services}: Pay for coaching, upgrades, and exclusive features
\end{itemize}

\begin{mfai-note}{Merit, Not Speculation}{faBalanceScale}
All \$MFAI tokens are traceable to on-chain achievements, not random airdrops. The protocol rewards validated learning, building, and governance.
\end{mfai-note}

\subsection{Sustainability Mechanisms}
\begin{itemize}
    \item \faFire\quad \textbf{Burn}: A portion of tokens used for premium actions is permanently burned (e.g., NFT minting, upgrades)
    \item \faSync\quad \textbf{Buyback}: Protocol revenues (subscriptions, NFT sales, project returns) fund regular \$MFAI buybacks
    \item \faLock\quad \textbf{Dynamic Staking}: Cognitive Lock\texttrademark{} with lock periods and ranking for influence and yield
    \item \faClock\quad \textbf{Intelligent Vesting}: Smart-contract enforced vesting for team and contributors
    \item \faUsers\quad \textbf{Community Fund}: Dedicated allocation for protocol growth and rewards
\end{itemize}

\begin{mfai-box}{A Closed-Loop, Antifragile Economy}{}
The \$MFAI token economy is designed for sustainability: value is driven by real activity, protocol adoption, and user reputation. Scarcity is enforced by burn and lock mechanisms, while buybacks and Neuro-Dividends\texttrademark{} redistribute value to active contributors.
\end{mfai-box}

\subsection{Token Allocation \& Vesting}

\begin{figure}[H]
\centering
\begin{tikzpicture}
% Pie or bar chart with vesting schedule (to be rendered)
\end{tikzpicture}
\caption{Token Allocation Breakdown: team, community, investors, ecosystem, reserves, vesting schedule}
\end{figure}

\begin{tblr}{@{} l l l l @{} }
\hline
\textbf{Tranche} & \textbf{Allocation} & \textbf{Vesting} & \textbf{Purpose} \\
\hline
Team & XX\% & 36m linear & Core development, alignment \\
Community & XX\% & 24m linear & Contributor rewards, growth \\
Investors & XX\% & 18m cliff+linear & Strategic partners \\
Ecosystem & XX\% & 12m linear & Grants, partnerships \\
Reserves & XX\% & Flexible & Protocol security, future needs \\
\hline
\end{tblr}

\subsection{Economic Trajectory}
\begin{mfai-box}{Antifragile, Meritocratic Growth}{}
The \$MFAI token grows in value as the ecosystem expands. Every module, credential, and governance action increases demand and reputation. No speculative promises: only \textbf{utility}, \textbf{proof}, and \textbf{sovereignty}.
\end{mfai-box}
