% ===========================================================================
% Executive Summary
% ===========================================================================

\section{Executive Summary}

\begin{mfai-box}{The Vision}{rocket}
Money Factory AI is not a Web2 platform with tokens. It is a Cognitive Activation Protocol™ designed to turn skill into capital, and builders into sovereign contributors.  
In an era where AI augments intelligence, Web3 redefines entrepreneurship, and decentralization reshapes governance, one thing is missing: a structured path to become an active protocol-native founder.  
Money Factory AI is that path.
\end{mfai-box}

\mfaithink{We don’t build for users. We activate entrepreneurs.}

\begin{mfai-box}{The Protocol in Action}{cogs}
MFAI is powered by a five-phase sovereignty loop that transforms intention into Proof, skill into capital, and contribution into governance rights.
\end{mfai-box}

\begin{mfai-phase}{1. Learn — Skillchain Mining™}
Builders follow a personalized journey designed by Zyno™, the AI Co-Founder™.  
Each mission completed yields:
\begin{itemize}
  \item A \textbf{Proof-of-Skill Token™} — verifiable, certifiable, stakable
  \item $MFAI tokens — earned via Skillchain Mining™
\end{itemize}
\end{mfai-phase}

\begin{mfai-phase}{2. Build — Proof-of-Vision™}
Builders create real MVPs: smart contracts, token economies, decentralized tools, etc.  
Each MVP is documented into a \textbf{Proof-of-Vision™}: a structured profile of their value, stack, and vision.
\end{mfai-phase}

\begin{mfai-phase}{3. Prove — Reputation through Contribution}
Mentor others. Validate skills. Co-create learning tracks.  
These actions fuel your \textbf{Proof Pass™}, an evolving on-chain identity that includes your skills, trust level, and governance weight.
\end{mfai-phase}

\begin{mfai-phase}{4. Activate — Synaptic Governance™}
With Proofs and tokens, builders can submit their projects to the protocol’s Launchpad.  
If accepted:
\begin{itemize}
  \item They gain access to protocol-funded tools
  \item Receive exposure, mentoring, and execution support
  \item Unlock advanced governance slots
\end{itemize}
\end{mfai-phase}

\begin{mfai-phase}{5. Scale — Stake, Vote, Earn}
By engaging in \textbf{Cognitive Lock™} (staking $MFAI), contributors:
\begin{itemize}
  \item Access governance
  \item Submit proposals
  \item Earn \textbf{Neuro-Dividends™} from protocol revenue
\end{itemize}
\end{mfai-phase}

\begin{mfai-box}{Key Value Propositions}{star}
\begin{itemize}
  \item \textbf{Proof-Based System:} Progress is certified and visible on-chain.
  \item \textbf{Zyno AI™:} A co-founder that evolves with each contributor.
  \item \textbf{Meritocratic Launchpad:} Projects rise by proof, not pitch decks.
  \item \textbf{Circular Token Economy:} Every action has real utility and feedback.
\end{itemize}
\end{mfai-box}

\begin{mfai-note}
MFAI is in pre-TGE phase. The platform is under construction by an active core team. Early contributors will be rewarded with upgradeable protocol Passes (Gold, Platinum, Diamond), unlocking tools, visibility, and governance access.
\end{mfai-note}

\mfaithink{From Skill to Sovereignty. Build Proof. Govern Value.}
