\section{Market Context \& Problem Statement}

\begin{mfai-box}{Definition: Cognitive Activation Market}{info-circle}
The cognitive activation market is where Web3 learning platforms, verifiable skill credentials, AI-driven mentoring, and decentralized contribution rewards intersect. In this emerging space, skills become programmable capital and contributors evolve into sovereign actors.
\end{mfai-box}

\vspace{1em}

\begin{mfai-box}{Why Now?}{question-circle}
In the current digital economy, talent remains undervalued. Web2 platforms monetize users without enabling true ownership, while Web3 protocols often fail to recognize and reward non-technical contributions. Meanwhile, AI amplifies productivity — but without frameworks for verifiable activation. MFAI responds to this fragmentation with a unified, on-chain activation protocol.
\end{mfai-box}

\vspace{1.5em}

\subsection*{Emerging Market Segments}

Although no official taxonomy yet defines this convergence, several fast-growing markets align with the building blocks of the MFAI protocol:

\begin{center}
\begin{tikzpicture}[
    pie/.style={text opacity=1},
]
    \pie[
        text=legend, 
        segment style/.style={
            draw=solana-purple,
            fill=solana-green!30,
            line width=0.8pt
        }
    ]{
        35/Verifiable Credentialing (Web3 \& EdTech)/\$4.5B,
        30/AI-Powered Learning Tools/\$3.9B,
        22/DAO-based Incentive Mechanisms/\$2.8B,
        13/On-chain Contribution Tracking/\$1.7B
    }

    \node[text=solana-purple, font=\bfseries\large] at (0,4) {Estimated Sector Breakdown (2028)};
\end{tikzpicture}
\end{center}

\vspace{1em}

\begin{tblr}{colspec={|X[0.52]|X[0.4]|}, hlines}
\textbf{Sector} & \textbf{Projected Size (2028)} \\
Verifiable Credentialing (EdTech, Web3) & \$4.5 billion \\
AI-Powered Learning Assistants & \$3.9 billion \\
DAO Incentivization Platforms & \$2.8 billion \\
On-chain Contribution Tracking & \$1.7 billion \\
\end{tblr}

\vspace{1em}

\begin{mfai-note}
Estimates based on synthesis of reports from Emergen Research (2024), Statista, Messari, Outlier Ventures and MarketsandMarkets. Segments are indicative and mapped to internal MFAI components: Proof-of-Skill™, Zyno™, Neuro-Dividends™, and Synaptic Governance™.
\end{mfai-note}

\vspace{2em}

\subsection*{A New Economic Stack}

\begin{center}
\begin{tikzpicture}[
  node distance=1.4cm,
  layer/.style={
    draw=solana-purple,
    fill=solana-purple!5,
    text centered,
    minimum height=1.2cm,
    text width=6.2cm,
    font=\bfseries\small,
    rounded corners=3pt
  }
]

\node[layer] (skills) {Cognitive Layer: Skills, Learning, Mentorship};
\node[layer, below=of skills] (proof) {Proof Layer: Credentials, Validation, Reputation};
\node[layer, below=of proof] (capital) {Capital Layer: Ownership, Tokens, Access};
\node[layer, below=of capital] (governance) {Governance Layer: Meritocratic Coordination};

\end{tikzpicture}
\end{center}

\vspace{1em}

\begin{mfai-note}
MFAI unifies these layers to create an on-chain protocol for transforming knowledge into capital, and contribution into collective governance.
\end{mfai-note}
