\section{Cognitive Activation Protocol™}
\subsection*{From Web2 to Web3 Sovereignty}

\begin{mfai-box}{Context: The Cognitive Web Transition}{exchange-alt}
The digital shift from Web2 to Web3 introduces more than new technologies — it demands a redefinition of value creation, proof, and ownership. MFAI answers this shift with a verifiable protocol for activating skills into capital.
\end{mfai-box}

\vspace{1em}

\subsection*{From Platform to Protocol}

Most Web2 platforms capture value created by users without returning sovereignty. Certificates are static. Contribution is invisible. Governance is absent. By contrast, MFAI transforms individuals into network-native builders, guided by their proof of skill, vision, and contribution.

\vspace{1em}

\begin{mfai-warning}
You don’t pitch. You prove. And your proof becomes capital.
\end{mfai-warning}

\vspace{1em}

\subsection*{Key Differences Between Web2 \& Web3 Activation Models}

\begin{tblr}{colspec={|X[1]|X[1]|X[1]|}, hlines}
\textbf{Aspect} & \textbf{Web2 Model} & \textbf{MFAI Web3 Model} \\
Identity & Centralized profiles & Sovereign, wallet-based identity \\
Skills & Offline diplomas & On-chain proof-of-skill tokens \\
Contribution & Invisible to system & Verifiable and rewarded \\
Ownership & Platform-owned content & User-owned capital and data \\
Governance & Platform decision-making & Synaptic DAO participation \\
AI Support & Absent or extractive & AI Co-Founder for user agency \\
\end{tblr}

\vspace{2em}

\subsection*{The MFAI Cognitive Activation Protocol™}

\begin{mfai-phase}{From Skillchains to Sovereignty}

The protocol is structured around six interconnected mechanisms:

\begin{itemize}
  \item \mfaiproof{Skillchain Mining™:} Validate knowledge through applied modules. Each skill becomes a unit of capital.
  \item \mfaiproof{Zyno – AI Co-Founder™:} A strategic AI partner that guides, accelerates, and optimizes each user’s path.
  \item \mfaiproof{Proof-of-Skill Tokens™:} On-chain attestations of competence, earned through learning and doing.
  \item \mfaiproof{Proof-of-Vision Incubator™:} Community-funded launchpad based on demonstrable contribution, not pitch decks.
  \item \mfaiproof{Synaptic Governance™:} Reputation-weighted decision making where proof gives voice and influence.
  \item \mfaiproof{Neuro-Dividends™:} Rewards tied to value creation — not speculation.
\end{itemize}

\end{mfai-phase}

\vspace{2em}

\subsection*{Visualizing the Activation Stack™}

\begin{center}
\begin{tikzpicture}[
  node distance=1.4cm,
  layer/.style={
    draw=solana-purple,
    fill=solana-purple!5,
    text centered,
    minimum height=1.2cm,
    text width=6.2cm,
    font=\bfseries\small,
    rounded corners=3pt
  }
]

\node[layer] (skills) {Skillchain Mining™ (Learn and Validate)};
\node[layer, below=of skills] (ai) {Zyno™ (AI Mentoring + Optimization)};
\node[layer, below=of ai] (proof) {Proof-of-Skill Tokens™};
\node[layer, below=of proof] (launch) {Proof-of-Vision Incubator™};
\node[layer, below=of launch] (governance) {Synaptic Governance™};
\node[layer, below=of governance] (rewards) {Neuro-Dividends™};

\end{tikzpicture}
\end{center}

\vspace{1em}

\begin{mfai-note}
This protocol turns learners into \mfaiword{Sovereign Builders™}, with AI-powered guidance, decentralized proof systems, and a regenerative value model.
\end{mfai-note}
