\section{Synaptic Governance™ — A Meritocratic Coordination Engine}

\begin{mfai-box}{Governance by Proof, Not Position}{balance-scale}
In the MFAI protocol, governance is not a privilege — it is a responsibility earned through verifiable contribution. Synaptic Governance™ rewards active builders, not passive holders.
\end{mfai-box}

\vspace{1em}

\subsection*{Governance Principles}

\begin{itemize}
  \item \mfaiproof{Proof-Weighted Voting:} Voting power is derived from verifiable skill, vision, and contribution — not simply token balance.
  \item \mfaiproof{Meritocratic DAO Design:} MFAI DAO members unlock proposal rights, voting tiers, and influence through proven action.
  \item \mfaiproof{Zyno-Guided Proposals:} Governance proposals are supported and audited by Zyno for clarity, compliance, and impact simulation.
\end{itemize}

\vspace{1em}

\subsection*{Layers of Synaptic Participation}

\begin{center}
\begin{tikzpicture}[
  node distance=1.2cm,
  layer/.style={
    draw=solana-cyan!60!black,
    fill=solana-cyan!10,
    font=\bfseries\small,
    text centered,
    text width=6.2cm,
    rounded corners=3pt,
    minimum height=1.2cm
  }
]

\node[layer] (observers) {Observers\\\scriptsize{Read-only or token holders}};
\node[layer, below=of observers] (contributors) {Contributors\\\scriptsize{With Proof-of-Skill/Contribution}};
\node[layer, below=of contributors] (governors) {Governors\\\scriptsize{Voting via merit and active staking}};
\node[layer, below=of governors] (core) {Core Architects\\\scriptsize{Elected by performance and Zyno-backed proposal history}};

\end{tikzpicture}
\end{center}

\vspace{1em}

\begin{mfai-note}
Synaptic Governance™ ensures that the protocol evolves with its most active minds — not its wealthiest wallets.
\end{mfai-note}

\vspace{1em}

\subsection*{Use of Governance}

\begin{itemize}
  \item Allocate treasury resources to builders and incubated projects.
  \item Approve or fork learning modules, staking rules, and incentive layers.
  \item Vote on tokenomics upgrades and roadmap shifts.
  \item Elect operational squads and validators.
\end{itemize}

\vspace{2em}

\begin{mfai-warning}
Protocols are political. MFAI makes that politics transparent, programmable, and merit-based — empowering contributors over capital.
\end{mfai-warning}
