\section{Proof-of-Vision Incubator™ — The Community Launch Engine}

\begin{mfai-box}{From Ideas to Initiatives}{rocket}
The MFAI Launchpad, branded as the \textbf{Proof-of-Vision Incubator™}, is where validated builders move from competence to creation. Projects are not selected through centralized curation — but activated through on-chain proof, peer evaluation, and community-backed funding.
\end{mfai-box}

\vspace{1em}

\subsection*{Incubation Based on Proof, Not Pitch}

Traditional startup launchpads rely on pitch decks and private deal flows. MFAI replaces this with transparent, proof-driven criteria:

\begin{itemize}
  \item \mfaiproof{Proof-of-Skill Tokens™:} Demonstrated ability to deliver in relevant domains.
  \item \mfaiproof{Proof-of-Vision™:} A structured project outline submitted on-chain via the incubator interface.
  \item \mfaiproof{Community Scoring:} Evaluation by Sovereign Builders™ and Zyno-assisted audits.
  \item \mfaiproof{Synaptic Governance Validation:} Final allocation of support through DAO voting or delegated squads.
\end{itemize}

\vspace{2em}

\subsection*{Incubation Flow — From Builder to Launch}

\begin{center}
\begin{tikzpicture}[
  node distance=1.4cm and 2cm,
  box/.style={
    draw=solana-yellow!80!black,
    fill=solana-yellow!10,
    font=\bfseries\small,
    text centered,
    text width=6.2cm,
    rounded corners=3pt,
    minimum height=1.2cm
  }
]

\node[box] (idea) {Idea Proposal (Proof-of-Vision™)};
\node[box, below=of idea] (review) {Community \& Zyno Review};
\node[box, below=of review] (vote) {DAO or Squad Validation};
\node[box, below=of vote] (funding) {Resource Allocation \& Smart Escrow};
\node[box, below=of funding] (launch) {Project Launch \& On-chain Tracking};

\draw[->, thick, color=solana-yellow!80!black] (idea) -- (review);
\draw[->, thick, color=solana-yellow!80!black] (review) -- (vote);
\draw[->, thick, color=solana-yellow!80!black] (vote) -- (funding);
\draw[->, thick, color=solana-yellow!80!black] (funding) -- (launch);

\end{tikzpicture}
\end{center}

\vspace{1.5em}

\subsection*{What Gets Incubated?}

\begin{itemize}
  \item Community tools and governance plugins for the MFAI protocol
  \item DePIN and DePAI primitives that align with our stack
  \item Edtech, AI, DAO or Web3 projects with verifiable builder proofs
\end{itemize}

\vspace{1.5em}

\begin{mfai-warning}
You don’t raise capital with slides — you raise it with skill, vision, and verified community alignment.
\end{mfai-warning}
