\section{Protocol Architecture, Token Utility \& Economic Viability}

\begin{mfai-box}{Overview}{cogs}
MFAI is not a single application — it is a layered infrastructure combining AI, Web3, and governance into a verifiable economy of skill and contribution. This section presents the architecture, token utility, financial design, and long-term sustainability mechanisms of the protocol.
\end{mfai-box}

\vspace{1.5em}

\subsection*{Token Utility — \$MFAI}

\begin{itemize}
  \item \mfaiproof{Proof-of-Stake:} Lock tokens via \textbf{Cognitive Lock™} to earn governance rights and access to premium features.
  \item \mfaiproof{Credential Minting:} Use \$MFAI to mint Proof-of-Skill™, Proof-of-Vision™, or Proof-of-Contribution™.
  \item \mfaiproof{Zyno Access:} Tiered Zyno capabilities (Mentor/Builder/Analyst mode) unlocked via token thresholds.
  \item \mfaiproof{Launchpad Entry:} Stake \$MFAI to activate your Proof-of-Vision proposal in the Incubator.
  \item \mfaiproof{DAO Participation:} Vote, propose, or join squads via proof-weighted token governance.
\end{itemize}

\vspace{1.5em}

\begin{mfai-note}
The \$MFAI token is not just a financial instrument — it’s the connective tissue of cognitive activation, reward distribution, and on-chain reputation.
\end{mfai-note}

\vspace{2em}

\subsection*{Burn, Buyback \& Treasury Design}

\begin{itemize}
  \item \mfaiproof{Buyback Triggers:} Revenue from Zyno Pro subscriptions and credential minting is partially redirected into buybacks.
  \item \mfaiproof{Burn Cycles:} DAO votes determine when excess tokens from unclaimed rewards are burned.
  \item \mfaiproof{Smart Escrow for Projects:} Treasury allocations to projects are time-locked and milestone-based.
  \item \mfaiproof{Elastic Treasury:} Income sources include NFT Passes (non-transferable credentials), SaaS revenue, and external contributions.
\end{itemize}

\begin{mfai-warning}
No speculative token emission. All supply mechanisms are tied to proof-based actions and ecosystem expansion.
\end{mfai-warning}

\vspace{2em}

\subsection*{Technical Architecture Overview}

\begin{itemize}
  \item \mfaiproof{Zyno Layer:} AEPO/AECO modules + Retrieval-Augmented Governance (RAG-Gov™).
  \item \mfaiproof{Skillchain Engine:} Tracks credentialable activities and peer validation trails.
  \item \mfaiproof{Governance Core:} DAO modules + delegated squads + proposal registry.
  \item \mfaiproof{Smart Modules:} Staking, vesting, rewards, and minting on EVM-compatible chains.
\end{itemize}

\vspace{1em}
\begin{mfai-note}
MFAI modules are interoperable, modular, and composable by design — ready for Layer 2 deployment and integration with DAO tooling standards.
\end{mfai-note}

\vspace{2em}

\subsection*{Financial Forecasts (2025–2028)}

\begin{tblr}{colspec={|X[0.6]|X[0.4]|}, hlines}
\textbf{Revenue Stream} & \textbf{2028 Proj. (USD)} \\
Zyno Subscriptions (B2C/B2B) & \$3.1M \\
Skillchain / Credential Minting Fees & \$2.5M \\
Launchpad/Incubator Revenue & \$1.2M \\
DAO Governance Services & \$850K \\
NFT Passes (one-time sales) & \$640K \\
\end{tblr}

\vspace{1em}
\textit{Note:} Forecasts assume 15\% quarterly user base growth and conservative adoption across 3 L2 networks.

\vspace{2em}

\subsection*{Risks \& Mitigation}

\begin{itemize}
  \item \mfaiproof{Market Volatility:} Mitigated by diversified revenue + protocol-native utility beyond speculation.
  \item \mfaiproof{Overcomplexity:} Reduced via Zyno onboarding, progressive disclosure and AI tooling.
  \item \mfaiproof{Low Governance Participation:} Addressed by reputation-based weight + Zyno voting assistants.
  \item \mfaiproof{AI Alignment:} Continuous evaluation of Zyno actions via cryptographic logs and reproducibility.
\end{itemize}

\vspace{1em}
\begin{mfai-warning}
MFAI is not risk-free — but its modular design, proof-centric economy, and AI-driven UX give it adaptive resilience.
\end{mfai-warning}

\vspace{2em}
\subsection*{Tokenomics \& DAO Synchronization}

\begin{mfai-box}{Tokenomics = Governance Infrastructure}{layer-group}
$MFAI$ is a utility + coordination token. Its supply, velocity, and allocation are tightly coupled to activation dynamics and protocol governance.
\end{mfai-box}

\vspace{1em}

\begin{itemize}
  \item \mfaiproof{Initial Distribution:}
    \begin{itemize}
      \item 30\% — Ecosystem Rewards (Skillchain Mining™, Zyno tasks)
      \item 20\% — Treasury \& DAO (grants, governance allocation)
      \item 18\% — Team \& Advisors (vested 3+ years)
      \item 15\% — Strategic Backers
      \item 10\% — Community Airdrops \& Activation Campaigns
      \item 7\% — Liquidity + Exchanges
    \end{itemize}
  \item \mfaiproof{Emission Rules:} All future emissions are \textbf{proof-triggered} — linked to real on-chain activity or proposal-based unlocks.
  \item \mfaiproof{Governance Sync:} Key DAO votes (e.g. funding, burn \%, treasury flows) are triggered automatically via proposal smart contracts.
\end{itemize}

\vspace{1em}
\begin{mfai-note}
This makes \$MFAI a self-regulating economic substrate — less speculation, more activation.
\end{mfai-note}

\vspace{2em}

\begin{center}
\begin{tikzpicture}[
  node distance=1.3cm,
  element/.style={
    draw=solana-purple!60,
    fill=solana-purple!10,
    font=\small\bfseries,
    text centered,
    text width=6cm,
    rounded corners=4pt,
    minimum height=1.1cm
  }
]

\node[element] (mine) {Skillchain Mining};
\node[element, below=of mine] (mint) {Credential Minting Fees};
\node[element, below=of mint] (buyback) {Buyback Allocation};
\node[element, below=of buyback] (dao) {DAO-Directed Emissions};
\node[element, below=of dao] (rewards) {Staking \& Contribution Rewards};

\draw[->, thick, color=solana-purple] (mine) -- (mint);
\draw[->, thick, color=solana-purple] (mint) -- (buyback);
\draw[->, thick, color=solana-purple] (buyback) -- (dao);
\draw[->, thick, color=solana-purple] (dao) -- (rewards);

\end{tikzpicture}
\end{center}

\vspace{2em}

\begin{mfai-warning}
Any protocol can issue a token. MFAI turns its token into programmable governance — each transaction reinforcing the proof-based loop.
\end{mfai-warning}

